---
title: "CSAIS Community Types"
author: "Jeremy Price"
date: "10/4/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggcorrplot)
library(treemapify)
library(shiny)
library(flexdashboard)
library(rmarkdown)
library(plotly)
library(splitstackshape)
library(readr)
library(scales)
library(ggplot2)
library(maps)
library(ggpubr)
library(ggrepel)
library(maps)
library(rsquaire)
library(usdata)
library(extrafont)
library(dplyr)
library(tidyr)
library(grid)
library(tools)
library(tilemaps)
library(sf)
library(png)
library(ggtext)
library(rcartocolor)
library(stringr)
library(zoo)
library(fontawesome)
library(forcats)
library(DT)
library(tibble)
library(calheatmapR)
library(ggTimeSeries)
library(imager)
library(ggwordcloud)
library(ggbeeswarm)
library(streamgraph)
library(htmltools)
library(leaflet)
library(leaflet.extras)
library(FactoMineR)
library(factoextra)
library(dygraphs)
library(xts)
library(stringr)
library(reactable)
library(ggalluvial)
library(knitr)
library(kableExtra)
library(glue)
```

```{r global} 
tags$style("@import url(https://use.fontawesome.com/releases/v5.8.2/css/all.css);")

usa.map <<- governors %>%
  mutate(tile_map = generate_map(geometry, square = FALSE, flat_topped = TRUE))

communities.list <- c("Big Cities",
                      "Centers of Socioeconomic Inequality",
                      "Diverse Small Cities",
                      "Diverse Suburban Jewish Centers",
                      "Mid-Sized City Republicans",
                      "Small Town Democrats",
                      "Suburban Jewish Centers",
                      "Wealthy Enclaves",
                      "White Republicans",
                      "White Suburbs")

colors.diverge <<- c("#006298", "#FAF7F2", "#056E41")
colors.iu.light <- c("#FF636A", "#FFA690", "#FFE694", "#A7D094", "#94D2E7", "#C09EBB", "#FFD6DB", "#C6ECF6", "#DEE8C6", "#DECADC")
colors.iu <- c("#990000", "#DF3603", "#FFAA00", "#056E41", "#006298", "#59264D", "#5A0C0C",
               "#00385F", "#004421", "#330D2B")

overall.frame <- read_csv("cluster_designations-10.csv")
sd.frame <- read_csv("sundown-cluster.csv")
just.cities <- overall.frame %>% select("cityID", "community_type") %>% na.omit

coded.frame <- read_csv("coded-incidents-full.csv")
coded.frame <- coded.frame %>% full_join(just.cities) %>% na.omit()


overall.frame$jewish_infrastructure <- rescale(overall.frame$jewish_infrastructure,
                                               to = c(-1, 1))
overall.frame$community_interaction <- rescale(overall.frame$community_interaction, to = c(0, 1))
overall.frame$diversity_index <- rescale(overall.frame$diversity_index, to = c(0, 1))
overall.frame$pop_category <- rescale(overall.frame$pop_category, to = c(0, 1))
overall.frame$political_scale <- rescale(overall.frame$political_scale, to = c(0, 1))
overall.frame$median_income <- rescale(overall.frame$median_income, to = c(0,1))

median.diversity <<- median(overall.frame$diversity_index)
income.median <<- median(overall.frame$median_income)
population.median <<- median(overall.frame$pop_category)
political.median <<- median(overall.frame$political_scale)
jewish.median <<- median(overall.frame$jewish_infrastructure)
community.median <<- median(overall.frame$community_interaction)

overall.frame <<- overall.frame %>% group_by(community_type) %>%
  mutate(diversity_median = median(diversity_index),
         income_median = median(median_income),
         population_median = median(pop_category),
         political_median = median(political_scale),
         jewish_median = median(jewish_infrastructure),
         community_median = median(community_interaction)) %>%
  na.omit() %>% ungroup()

sundown.frame <- overall.frame %>% filter(cityID %in% sd.frame$cityID) %>%
  select(cityID, community_type, community_interaction, diversity_index,
         median_income, jewish_infrastructure, political_median,
         population_median)

just.cities <- just.cities[!(just.cities$cityID == "ia-bettendorf" | just.cities$cityID == "ia-des moines"),]
variables.key <- c(community_median = "Community Interaction",
                   diversity_median = "Diversity Level",
                   income_median = "Median Income",
                   jewish_median = "Jewish Infrastructure",
                   political_median = "Politics",
                   population_median = "Population")
months.key <- c(Jan = "01", Feb = "02", Mar = "03", Apr = "04", May = "05", Jun = "06",
                Jul = "07", Aug = "08", Sep = "09", Oct = "10", Nov = "11", Dec = "12")
months.list <- c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug",
                 "Sep", "Oct", "Nov", "Dec")
seasons.list <- c("Winter", "Spring", "Summer", "Fall")
cities.frame <- read_csv("list-incidents-cities.csv", col_names = TRUE)
cities.frame$cityID <- paste(cities.frame$state, cities.frame$city, sep = "-")
cities.frame$cityID <- tolower(cities.frame$cityID)
months.frame <- cities.frame %>% right_join(overall.frame) %>%
  select(cityID, community_type, date)
#months.frame$date <- months.frame$date %>% as.yearmon("2016-01-01") #as.yearmon(seq(ISOdate(2016,1,1), by = "month", length.out = 48))
months.frame <- months.frame %>% separate(date, into = c("year", "month"))
#months.frame$month <- recode(months.frame$month, !!!months.key)
#months.frame$date <- paste(months.frame$year, months.frame$month, sep = "-")
months.frame$date <- paste("01", months.frame$month, months.frame$year, sep = "-")
months.frame <- months.frame %>% group_by(community_type) %>% count(date) %>% ungroup()
months.overall <- months.frame %>% select(date, n)
#months.overall <- months.overall %>% separate(date, into = c("month", "year"))
avg.frame <- months.frame %>% group_by(date) %>% summarize(n = mean(n))
#avg.frame <- avg.frame %>% rename("avg" = "n")
avg.frame$community_type <- "avg"
total.community.count <- length(unique(overall.frame$cityID))
average.incidence.rate <- length(coded.frame$adl_id) / total.community.count / 47

#months.frame$date <- as.Date(months.frame$date, "%d-%m-%Y")
#months.frame <- months.frame %>%
#  pivot_wider(names_from = community_type, values_from = n)
#months.frame[is.na(months.frame)] <- 0
months.overall <- as.data.frame(months.overall) %>% group_by(date) %>% tally(n) %>% ungroup()
months.overall$date <- as.Date(months.overall$date, "%d-%m-%Y")
months.xts <- as.xts(months.overall, order.by = months.overall$date)
#ct.xts <- as.xts(months.frame, order.by = months.frame$date)

usa_states <- map_data("state")
usa <- ggplot(usa_states, aes(x = long, y = lat)) +
  geom_polygon(aes(group = group), color = "#A7A9AB",
               fill = "#EDEBEB", size = 0.2) +
  coord_quickmap()

nature.frame <- read_csv("nature-count-type.csv", col_names = TRUE) %>%
  pivot_longer(cols = !community_type)
type.wide.frame <- read_csv("type-count-type.csv", col_names = TRUE)
type.frame <- type.wide.frame %>% pivot_longer(cols = !community_type)
type.levels <- c("Vandalism", "Harassment", "Cyberbullying", "Performance", "Literature Dump", "Bomb Threat", "Not Specified")
nature.levels <- c("Nazi", "General Antisemitism", "Oppression Connection", "Money", "Holocaust Denial", "Conspiracy", "Israel", "Not Specified")
nature.key <- c(nazi = "Nazi", general_antisemitism = "General Antisemitism",
                oppression_connection = "Oppression Connection", israel = "Israel",
                money = "Money", conspiracy = "Conspiracy",
                holocaust_denial = "Holocaust Denial")
type.key <- c(type_vandalism = "Vandalism", type_harassment = "Harassment",
              type_cyberbullying = "Cyberbullying", type_performance = "Performance",
              type_literature_dump = "Literature Dump", type_bomb_threat = "Bomb Threat",
              type_not_specified = "Not Specified")
nature.frame$name <- recode(nature.frame$name, !!!nature.key)
nature.frame <- nature.frame %>% mutate(name = factor(name, levels = nature.levels))
type.frame$name <- recode(type.frame$name, !!!type.key)
type.frame <- type.frame %>% mutate(name = factor(name, levels = type.levels))

nt.frame <<- coded.frame %>% select(community_type, Nature, Type) %>%
  group_by(community_type, Nature, Type) %>% add_tally() %>% ungroup() %>% distinct()
nt.frame <- nt.frame %>% mutate(Nature = factor(Nature, levels = nature.levels))
nt.frame <- nt.frame %>% mutate(Type = factor(Type, levels = type.levels))

cluster.frame <- overall.frame %>% select(cityID, diversity_index, pop_category,
                                          median_income, political_scale,
                                          jewish_infrastructure, community_interaction) %>%
  column_to_rownames(var = "cityID")
cluster.frame$diversity_index <- scale(cluster.frame$diversity_index)
cluster.frame$pop_category <- scale(cluster.frame$pop_category)
cluster.frame$median_income <- scale(cluster.frame$median_income)
cluster.frame$political_scale <- scale(cluster.frame$political_scale)
cluster.frame$jewish_infrastructure <- scale(cluster.frame$jewish_infrastructure)
cluster.frame$community_interaction <- scale(cluster.frame$community_interaction)
mds <- cluster.frame %>%
  dist() %>%          
  cmdscale() %>%
  as_tibble()
mds <- mds %>%
  mutate(groups = as.factor(overall.frame$community_type))
colnames(mds) <- c("dim.1", "dim.2", "community_type")
mds$cityID <- just.cities$cityID
#mds$dim.1 <- -mds$dim.1
#mds$dim.2 <- -mds$dim.2
# Plot and color by groups
#scatter <- ggscatter(mds, x = "dim.1", y = "dim.2",
#                     label = overall.frame$cityID,
#                     color = "Community Type",
#                     palette = colors.iu,
#                     size = 0.75,
#                     ellipse = TRUE,
#                     ellipse.type = "convex",
#                     repel = TRUE,
#                     font.family = "Open Sans") +
#  bgcolor("#F7F7F8") +
#  guides(color = guide_legend(nrow = 3)) +
#  scale_x_continuous(name = "Urbanization", breaks = c(-2, 2),
#                     labels = c("Less", "More")) +
#  scale_y_continuous(name = "Jewish Centrality", breaks = c(-6, 2),
#                     labels = c("Less", "More")) +
#  theme(axis.text = element_text(color = "#243142"),
#        axis.ticks = element_line(color = "#243142"),
#        axis.line = element_line(color = "#243142"),
        #plot.background = element_rect(fill = "#FAF7F2"),
#        legend.background = element_rect(fill = NA),
#        legend.position = "bottom", legend.title = element_blank())

measures.plot <- function(var.community) {
  graph.frame <- overall.frame %>% filter(community_type == var.community) %>%
    select(community_type, income_median, diversity_median, population_median, political_median,
           jewish_median, community_median)
  graph.frame$diversity_median <- graph.frame$diversity_median - median.diversity
  graph.frame$jewish_median <- graph.frame$jewish_median - jewish.median
  graph.frame$population_median <- graph.frame$population_median - population.median
  graph.frame$income_median <- graph.frame$income_median - income.median
  graph.frame$political_median <- graph.frame$political_median - political.median
  graph.frame$community_median <- graph.frame$community_median - community.median
  graph.frame <- graph.frame %>% pivot_longer(cols = !community_type, names_to = "measure") %>%
    distinct()
  graph.frame$value_group <- factor(case_when(graph.frame$value < -0.1 ~ "low",
                                              graph.frame$value > 0.1 ~ "high",
                                              TRUE ~ "middle"),
                                    levels = c("low", "middle", "high"))
  variable.key <- c("community_median" = "Community Type",
                    "diversity_median" = "Diversity Level",
                    "income_median" = "Income Level",
                    "jewish_median" = "Jewish Infrastructure",
                    "political_median" = "Political Scale",
                    "population_median" = "Population")
  graph.frame$measure <- recode(graph.frame$measure, !!!variable.key)
  the.plot <- ggbarplot(graph.frame, x = "measure", y = "value",
                        color = "#b5c8b8", fill = "value_group",
                        palette = colors.diverge, #c("#006298", "#ffffff", "#990000"),
                        order = c("Population", "Political Scale",
                                  "Jewish Infrastructure", "Income Level",
                                  "Diversity Level", "Community Type")) +
    #title = plot.title,
    #subtitle = sub.title,
    #caption = cap.title) + 
    scale_y_continuous(limits = c(-0.85, 0.85)) +
    geom_hline(yintercept = 0, linetype = 2, color = "#79a7ac") +
    theme(axis.text.x = element_blank(),
          axis.text.y = element_text(color = "#243142", family = "Monoid"),
          axis.title = element_blank(),
          axis.ticks = element_blank(),
          axis.line = element_line(color = "#b5c8b8"),
          legend.position = "none",
          panel.grid.major = element_line(color = "#edeac2", linetype = 8)) +
    rotate()
  return(the.plot)
}

community.counts <- c(length(which(overall.frame$community_type == "Big Cities")),
                      length(which(overall.frame$community_type == "Centers of Socioeconomic Inequality")),
                      length(which(overall.frame$community_type == "Diverse Small Cities")),
                      length(which(overall.frame$community_type == "Diverse Suburban Jewish Centers")),
                      length(which(overall.frame$community_type == "Mid-Sized City Republicans")),
                      length(which(overall.frame$community_type == "Small Town Democrats")),
                      length(which(overall.frame$community_type == "Suburban Jewish Centers")),
                      length(which(overall.frame$community_type == "Wealthy Enclaves")),
                      length(which(overall.frame$community_type == "White Republicans")),
                      length(which(overall.frame$community_type == "White Suburbs")))

community.icons <<- data.frame(community_type = communities.list,
                              icons = c("fas fa-city",
                                        "fa-not-equal",
                                        "fas fa-palette",
                                        "fas fa-hamsa",
                                        "fas fa-industry",
                                        "fas fa-mountain",
                                        "fas fa-torah",
                                        "fas fa-funnel-dollar",
                                        "fas fa-compress-arrows-alt",
                                        "fa-archway"),
                              counts = community.counts,
                              colors = colors.iu,
                              light_colors = colors.iu.light)

map.frame <- overall.frame %>%
  select(community_type, cityID, lat, lon) %>%
  rename("longitude" = "lon", "latitude" = "lat") %>%
  separate(cityID, into = c("state","city"), sep = "-", remove = FALSE)
map.frame$city <- toTitleCase(map.frame$city)
map.frame$state <- toupper(map.frame$state)
map.frame$label <- paste(map.frame$city, map.frame$state, sep = ", ")

icon.frame <- data.frame(community_type = c("Big Cities", "Centers of Socioeconomic Inequality",
                                            "Diverse Small Cities", "Diverse Suburban Jewish Centers",
                                            "Mid-Sized City Republicans", "Small Town Democrats",
                                            "Suburban Jewish Centers", "Wealthy Enclaves",
                                            "White Republicans", "White Suburbs"),
                         icon = c("fa-city", "fa-not-equal", "fa-palette", "fa-hamsa",
                                  "fa-industry", "fa-mountain", "fa-torah", "fa-funnel-dollar",
                                  "fa-compress-arrows-alt", "fa-archway"),
                         extraClasses = c("fas", "fa", "fas", "fas", "fas", "fas",
                                          "fas", "fas", "fas", "fas"),
                         markerColor = c("#990000", "#DF3603", "#FFAA00", "#056E41",
                                         "#006298", "#59264D", "#800000", "#004F80",
                                         "#005C31", "#48183D"))

#map.frame <- map.frame %>% right_join(icon.frame)
IconSet <- awesomeIconList(
  "Big Cities" = makeAwesomeIcon(icon= "city", extraClasses = "fas", library = "fa",
                                 markerColor = "red", iconColor = "black"),
  "Centers of Socioeconomic Inequality" = makeAwesomeIcon(markerColor = "orange", icon= "not-equal",
                                                          library = "fa", iconColor = "black"),
  "Diverse Small Cities" = makeAwesomeIcon(icon= "palette", extraClasses = "fas", library = "fa", markerColor = "beige", iconColor = "black"),
  "Diverse Suburban Jewish Centers" = makeAwesomeIcon(icon= "hamsa", extraClasses = "fas", library = "fa", markerColor = "green", iconColor = "black"),
  "Mid-Sized City Republicans" = makeAwesomeIcon(icon= "industry", extraClasses = "fas", library = "fa", markerColor = "blue", iconColor = "black"),
  "Small Town Democrats" = makeAwesomeIcon(icon= "fa-mountain", extraClasses = "fas", library = "fa", markerColor = "purple", iconColor = "black"),
  "Suburban Jewish Centers" = makeAwesomeIcon(icon= "fa-torah", extraClasses = "fas", library = "fa", markerColor = "darkred", iconColor = "black"),
  "Wealthy Enclaves" = makeAwesomeIcon(icon= "fa-funnel-dollar", extraClasses = "fas", library = "fa", markerColor = "darkblue", iconColor = "black"),
  "White Republicans" = makeAwesomeIcon(icon= "fa-compress-arrows-alt", extraClasses = "fas", library = "fa", markerColor = "darkgreen", iconColor = "black"),
  "White Suburbs" = makeAwesomeIcon(icon= "fa-archway", extraClasses = "fas", library = "fa", markerColor = "darkpurple", iconColor = "black")
)

markerLegendHTML <- function(IconSet) {
    # container div:
    legendHtml <- "<div style='padding: 10px; padding-bottom: 10px;'><h4 style='padding-top:0; padding-bottom:10px; margin: 0;'>Legend </h4>"

    n <- 1
    # add each icon for font-awesome icons icons:
    for (Icon in IconSet) {
        if (Icon[["library"]] == "fa") {
        legendHtml<- paste0(legendHtml, "<div style='width: auto; height: 36px'>",
                             "<div style='position: relative; display: inline-block; width: 36px; height: 36px' class='awesome-marker-icon-",Icon[["markerColor"]]," awesome-marker'>",
                               "<i style='margin-left: 6px; margin-top: 9px; 'class= 'fa fa-",Icon[["icon"]]," fa-inverse'></i>",
                             "</div>",
                             "<p style='position: relative; top: 10px; display: inline-block; ' >", names(IconSet)[n] ,"</p>",
                           "</div>")    
        }
        n <- n + 1
    }
    paste0(legendHtml, "</div>")
}

create.map <- function(df) {
  the.map <- df %>%
    leaflet() %>%
    addTiles() %>%  # Add default OpenStreetMap map tiles
    addAwesomeMarkers(lng = df$latitude, lat = df$longitude,
                      popup = df$label, icon = ~IconSet[community_type]) %>%
    addControl(html = markerLegendHTML(IconSet = IconSet), position = "bottomright")
  return(the.map)
}

overall.map <- create.map(map.frame)

create.title <- function(ct) {
  the.icon <- community.icons$icons[community.icons$community_type == ct]
  the.color <- community.icons$colors[community.icons$community_type == ct]
  the.count <- community.icons$counts[community.icons$community_type == ct]
  the.caption <- paste0("There are ", the.count, " communities identified as ", ct)
  valueBox(ct, icon = the.icon, caption = the.caption, ct)
}

create.cloud <- function(ct) {
    cloud.frame <- coded.frame %>% filter(community_type == ct) %>%
    select(Type, Nature)
  nature.list <- cloud.frame$Nature
  type.list <- cloud.frame$Type
  cloud.list <- c(nature.list, type.list)
  use.frame <- data.frame(code = cloud.list)
  use.frame <- use.frame %>% group_by(code) %>% tally() %>% drop_na()
  use.frame$code <- str_replace(use.frame$code, "General Antisemitism", "General")
  incidents.cloud <- ggplot(use.frame, aes(label = code, size = n, color = n)) +
    geom_text_wordcloud_area(family = "Public Sans") +
    scale_size_area(max_size = 24) +
    scale_color_steps(low = community.icons$light_colors[community.icons$community_type == ct], high = community.icons$colors[community.icons$community_type == ct]) +
    theme(plot.background = element_rect(fill = "#F7F7F8"),
          panel.background = element_blank())
 return(incidents.cloud)
}

create.tilemap <- function(ct) {
    plot.frame <- coded.frame %>% filter(community_type == ct) %>%
      select(community_type, Type, Nature)
  incidents.count <- plot.frame %>% group_by(community_type, Type, Nature) %>% add_tally() %>% drop_na() %>% distinct()
  type.levels <- c("Vandalism", "Harassment", "Cyberbullying", "Performance", "Literature Dump", "Bomb Threat", "Not Specified")
  nature.levels <- c("Nazi", "General Antisemitism", "Oppression Connection", "Money", "Holocaust Denial", "Conspiracy", "Israel", "Not Specified")
  incidents.count <- incidents.count %>% mutate(Type = factor(Type, levels = type.levels)) %>%
    mutate(Nature = factor(Nature, levels = nature.levels))
  
  incidents.plot <- ggplot(incidents.count, aes(Type, Nature)) +
    geom_tile(aes(fill = n), color = "#243142") +
    geom_text(aes(label = n), size = 3)  +
    scale_fill_steps(low = "#EDEBEB", high = "#990000", name = "Number", na.value = "#F7F7F8") +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          title = element_blank(),
          axis.title = element_blank(),
          axis.text.x = element_text(angle = 90),
          legend.position = "bottom",
          text = element_text(family = "Open Sans"))
  return(incidents.plot)
}

create.calendar <- function(ct) {
  full.cal <- data.frame(community_type = ct,
                         year = c("2016", "2016", "2016", "2016", "2016",
                                  "2016", "2016", "2016", "2016", "2016",
                                  "2016", "2016", "2017", "2017", "2017",
                                  "2017", "2017", "2017", "2017", "2017",
                                  "2017", "2017", "2017", "2017", "2018",
                                  "2018", "2018", "2018", "2018", "2018",
                                  "2018", "2018", "2018", "2018", "2018",
                                  "2018", "2019", "2019", "2019", "2019",
                                  "2019", "2019", "2019", "2019", "2019",
                                  "2019", "2019", "2019"),
                         month = c("Jan", "Feb", "Mar", "Apr", "May", "Jun",
                                   "Jul", "Aug", "Sep", "Oct", "Nov", "Dec",
                                   "Jan", "Feb", "Mar", "Apr", "May", "Jun",
                                   "Jul", "Aug", "Sep", "Oct", "Nov", "Dec",
                                   "Jan", "Feb", "Mar", "Apr", "May", "Jun",
                                   "Jul", "Aug", "Sep", "Oct", "Nov", "Dec",
                                   "Jan", "Feb", "Mar", "Apr", "May", "Jun",
                                   "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))
  the.time <- months.frame %>% filter(community_type == ct) %>%
    separate(date, into = c("year", "month", "day")) %>%
    select(-day)
  the.time$month <- case_when(the.time$month == "01" ~ "Jan",
                              the.time$month == "02" ~ "Feb",
                              the.time$month == "03" ~ "Mar",
                              the.time$month == "04" ~ "Apr",
                              the.time$month == "05" ~ "May",
                              the.time$month == "06" ~ "Jun",
                              the.time$month == "07" ~ "Jul",
                              the.time$month == "08" ~ "Aug",
                              the.time$month == "09" ~ "Sep",
                              the.time$month == "10" ~ "Oct",
                              the.time$month == "11" ~ "Nov",
                              the.time$month == "12" ~ "Dec")
  the.time <- the.time %>%
    full_join(full.cal)# %>%
  the.time$n <- the.time$n %>% replace_na(0)
  season.colors <- c("#96B3DF", "#65AF58", "#E1C6B3", "#750C1A")
  the.avg <- the.time %>%
    group_by(month) %>%
    summarize(avg = mean(n))
  the.avg <- the.avg %>%
    mutate(month = factor(month, levels = months.list))
  the.max <- max(the.avg$avg) + 1
  time.plot <- ggplot(the.avg, aes(x = month, y = avg)) +
    geom_bar(stat = "identity", position = "dodge", aes(fill = avg)) +
    scale_fill_steps(low = "#EDEBEB", high = community.icons$colors[community.icons$community_type == ct], name = "Number", na.value = "#F7F7F8") +
    coord_polar(start = 0) +
    ylim(-2, the.max) +
    geom_bar(stat = "identity", aes(x = month, y = -2), fill = "white") +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          title = element_blank(),
          axis.title = element_blank(),
          axis.ticks = element_blank(),
          axis.text.y = element_blank(),
          text = element_text(family = "Open Sans"),
          legend.position = "bottom",
          panel.background = element_rect(fill = "white"))
  #time.plot <- ggplot(the.time, aes(x = date, y = n)) +
  #  stat_occurrence(color = community.icons$colors[community.icons$community_type == input$community_type]) +
  #  theme(panel.grid.major = element_blank(),
  #        panel.grid.minor = element_blank(),
  #        title = element_blank(),
  #        axis.title = element_blank(),
  #        text = element_text(family = "Monoid"),
  #        panel.background = element_rect(fill = "#F7F7F8"))
  return(time.plot)
}

create.hex <- function(ct) {
    m.frame <- overall.frame %>% filter(community_type == ct) %>%
    select(cityID, color, lat, lon) %>%
    separate(cityID, into = c("abbreviation","city"), sep = "-", remove = FALSE)
  m.frame$city <- toTitleCase(m.frame$city)
  m.frame$abbreviation <- toupper(m.frame$abbreviation)
  count.frame <- m.frame %>% count(abbreviation)
  the.map <- usa.map %>% full_join(count.frame) 
  hex.map <- ggplot(the.map) +
    geom_sf(aes(geometry = tile_map, fill = n), color = "#A7A9AB") +
    geom_sf_text(aes(geometry = tile_map, label = abbreviation),
                 fun.geometry = function(x) st_centroid(x), family = "Public Sans") +
    #scale_fill_gradient(low = "#EDEBEB", high = "#990000", name = "Number", na.value = "#F7F7F8") +
    scale_fill_steps(low = "#EDEBEB", high = community.icons$colors[community.icons$community_type == ct], name = "", na.value = "#F7F7F8") +
    theme_void() +
    theme(legend.position = "bottom",
          text = element_text(family = "Open Sans"))
  return(hex.map)
  hex.map
}

create.tile <- function(ct) {
  nt.frame <- nt.frame %>% filter(community_type == ct)
  incidents.plot <- ggplot(nt.frame, aes(Type, Nature)) +
    geom_tile(aes(fill = n), color = "#243142") +
    geom_text(aes(label = n), size = 3) +
    #scale_fill_gradient(low = "#EDEBEB", high = "#990000", name = "Number", na.value = "#F7F7F8") +
    scale_fill_steps(low = "#EDEBEB", high = community.icons$colors[community.icons$community_type == ct], name = "Number", na.value = "#F7F7F8") +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          title = element_blank(),
          axis.title = element_blank(),
          axis.text.x = element_text(angle = 45),
          legend.position = "bottom",
          text = element_text(family = "Open Sans"))
  incidents.plot <- ggplotly(incidents.plot)
  return(incidents.plot)
}

create.tile_agents <- function(ct) {
  plot.frame <- coded.frame %>% filter(community_type == ct) %>%
    select(community_type, Perpetrator, Target)
  incidents.count <- plot.frame %>% group_by(Perpetrator, Target) %>% add_tally() %>% drop_na() %>% distinct()
  target.levels <- c("Not Specified", "Student", "School", "Teacher", "Outsider", "Parent", "School Personnel")
  perpetrator.levels <- c("Not Specified", "Student", "Outsider", "Teacher", "Parent", "Crowd", "School Personnel")
  incidents.plot <- ggplot(incidents.count, aes(Perpetrator, Target)) +
    geom_tile(aes(fill = n), color = "#243142") +
    geom_text(aes(label = n), size = 3) +
    #scale_fill_gradient(low = "#EDEBEB", high = "#990000", name = "Number", na.value = "#F7F7F8") +
    scale_fill_steps(low = "#EDEBEB", high = community.icons$colors[community.icons$community_type == ct], name = "Number", na.value = "#F7F7F8") +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          title = element_blank(),
          axis.title = element_blank(),
          axis.text.x = element_text(angle = 45),
          legend.position = "bottom",
          text = element_text(family = "Open Sans"))
  incidents.plot <- ggplotly(incidents.plot)
  return(incidents.plot)
}

create.table <- function(ct) {
  table.frame <- overall.frame %>% filter(community_type == ct) %>%
    select(community_type, community_median, diversity_median, income_median,
           jewish_median, political_median, population_median) %>%
  distinct() %>% pivot_longer(!community_type) %>% select(-community_type)
  table.frame$adj <- NA
  table.frame[1, 3] <- table.frame[1, 2] - community.median
  table.frame[2, 3] <- table.frame[2, 2] - median.diversity
  table.frame[3, 3] <- table.frame[3, 2] - income.median
  table.frame[4, 3] <- table.frame[4, 2] - jewish.median
  table.frame[5, 3] <- table.frame[5, 2] - political.median
  table.frame[6, 3] <- table.frame[6, 2] - population.median
  table.frame$desc <- NA
  table.frame[1, 4] <- case_when(table.frame[1, 3] < -0.1 ~ '<i class="fa-building"></i> More Urban',
                                 table.frame[1, 3] > 0.1 ~  '<i class="fa-home"></i> More Rural',
                                 TRUE ~ '<i class="fas fa-ban"></i> N/A')
#                   '<i class="fab fa-hornbill"></i> High Diversity',
#                   '<i class="fas fa-money-bill-wave-alt"></i> Low Median Income',
#                   '<i class="fas fa-ban"></i> N/A',
#                   '<i class="fas fa-ban"></i> N/A',
#                   '<i class="fa fa-users"></i> High Population')
  table.frame <- table.frame %>% rename("Measure" = "name", "Median Score" = "value",
                                "Adjusted Score" = "adj", "Description" = "desc")
  table.table <- knitr::kable(table.frame)
  return(table.table)
}
```

# Overview

Antisemitic incidents in schools are a widespread and pervasive phenomenon. The [Anti-Defamation League](https://www.adl.org/) has reported a three-fold increase in school-based antisemitic incidences between 2015 and 2018, and a nearly two-fold increase in violent and non-violent incidences of antisemitism in general nationwide.

This project utilizes data from the [ADL H.E.A.T. Map](https://www.adl.org/education-and-resources/resource-knowledge-base/adl-heat-map) between 2016 and 2019 to identify incidents of antisemitism that specifically took place in schools. These incidents in schools are influenced by demographic, historical, social, and political factors. This project brings this data together to construct a community typology at the national level. This typology will provide insight into the ways that school-based incidents of hate are enacted and reported in context.

Developing a community typology will allow providers to better target specific demographic, historical, and political attributes of the communities in which these incidents occur through curriculum and learning experiences.

